%\begin{enumerate}
%\renewcommand{\labelenumi}{\textbf{\theenumi}.}
%\setlength{\leftmargin}{0pt}

\newcounter{itemcounter}
\begin{list}
{\textbf{\arabic{itemcounter}.}}
{\usecounter{itemcounter}\leftmargin=1.4em}
\setlength{\itemsep}{0cm}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}

\item \bf Olav Kongas. \it Nonlinear Dynamics in Modeling Cardiac Arrhytmias. \sf 1998.

\item \bf Kalju Vanatalu. \it Optimization of Processes of Microbial
  Biosynthesis of Isotopically Labeled Biomolecules and Their
  Complexes. \sf 1999.

\item \bf Ahto Buldas. \it An Algebraic Approach to the Structure of
  Graphs. \sf 1999.

\item \bf Monika Drews. \it A Metabolic Study of Insect Cells in Batch and
  Continuous Culture: Application of Chemostat and Turbidostat to the
  Production of Recombinant Proteins. \sf 1999.

\item \bf Eola Valdre. \it Endothelial-Specific Regulation of Vessel
  Formation: Role of Receptor Tyrosine Kinases. \sf 2000.

\item \bf Kalju Lott. \it Doping and Defect Thermodynamic Equilibrium in
  ZnS. \sf 2000.

\item \bf Reet Koljak. \it Novel Fatty Acid Dioxygenases from the Corals
  Plexaura homomalla and Gersemia fruticosa. \sf 2001.

\item \bf Anne Paju. \it Asymmetric oxidation of Prochiral and Racemic Ketones
  by Using Sharpless Catalyst. \sf 2001.

\item \bf Marko Vendelin. \it Cardiac Mechanoenergetics in silico. \sf 2001.

\item \bf Pearu Peterson. \it Multi-Soliton Interactions and the Inverse
  Problem of Wave Crest. \sf 2001.

\item \bf Anne Menert. \it Microcalorimetry of Anaerobic Digestion. \sf 2001.

\item \bf Toomas Tiivel. \it The Role of the Mitochondrial Outer Membrane in
  in vivo Regulation of Respiration in Normal Heart and Skeletal
  Muscle Cell. \sf 2002.

\item \bf Olle Hints. \it Ordovician Scolecodonts of Estonia and Neighbouring
  Areas: Taxonomy, Distribution, Palaeoecology, and Application. \sf 2002.

\item \bf Jaak N\~olvak. \it Chitinozoan Biostratigrapy in the Ordovician of
  Baltoscandia. \sf 2002.

\item \bf Liivi Kluge. \it On Algebraic Structure of Pre-Operad. \sf 2002.

\item \bf Jaanus Lass. \it Biosignal Interpretation: Study of Cardiac
  Arrhytmias and Electromagnetic Field Effects on Human Nervous
  System. \sf 2002.

\item \bf Janek Peterson. \it Synthesis, Structural Characterization and
  Modification of PAMAM Dendrimers. \sf 2002.

\item \bf Merike Vaher. \it Room Temperature Ionic Liquids as Background
  Electrolyte Additives in Capillary Electrophoresis. \sf 2002.

\item \bf Valdek Mikli. \it Electron Microscopy and Image Analysis Study of
  Powdered Hardmetal Materials and Optoelectronic Thin Films. \sf 2003.

\item \bf Mart Viljus. \it The Microstructure and Properties of Fine-Grained
  Cermets. \sf 2003.

\item \bf Signe Kask. \it Identification and Characterization of Dairy-Related
  Lactobacillus. \sf 2003

\item \bf Tiiu-Mai Laht. \it Influence of Microstructure of the Curd on
  Enzymatic and Microbiological Processes in Swiss-Type Cheese. \sf 2003.

\item \bf Anne Kuusksalu. \it 2–5A Synthetase in the Marine Sponge Geodia
  cydonium. \sf 2003.

\item \bf Sergei Bereznev. \it Solar Cells Based on Polycristalline
  Copper-Indium Chalcogenides and Conductive Polymers. \sf 2003.

\item \bf Kadri Kriis. \it Asymmetric Synthesis of C2-Symmetric Bimorpholines
  and Their Application as Chiral Ligands in the Transfer
  Hydrogenation of Aromatic Ketones. \sf 2004.

\item \bf Jekaterina Reut. \it Polypyrrole Coatings on Conducting and
  Insulating Substracts. \sf 2004.

\item \bf Sven N\~omm. \it Realization and Identification of Discrete-Time
  Nonlinear Systems. \sf 2004.

\item \bf Olga Kijatkina. \it Deposition of Copper Indium Disulphide Films by
  Chemical Spray Pyrolysis. \sf 2004.

\item \bf Gert Tamberg. \it On Sampling Operators Defined by Rogosinski, Hann
  and Blackman Windows. \sf 2004.

\item \bf Monika \"Ubner. \it Interaction of Humic Substances with Metal
  Cations. \sf 2004.

\item \bf Kaarel Adamberg. \it Growth Characteristics of Non-Starter Lactic
  Acid Bacteria from Cheese. \sf 2004.

\item \bf Imre Vallikivi. \it Lipase-Catalysed Reactions of
  Prostaglandins. \sf 2004.

\item \bf Merike Peld. \it Substituted Apatites as Sorbents for Heavy
  Metals. \sf 2005.

\item \bf Vitali Syritski. \it Study of Synthesis and Redox Switching of
  Polypyrrole and Poly(3,4-ethylenedioxythiophene) by Using in-situ
  Techniques. \sf 2004.

\item \bf Lee P\~ollumaa. \it Evaluation of Ecotoxicological Effects Related
  to Oil Shale Industry. \sf 2004.

\item \bf Riina Aav. \it Synthesis of 9,11-Secosterols Intermediates. \sf 2005.

\item \bf Andres Braunbr\"uck. \it Wave Interaction in Weakly Inhomogeneous
  Materials. \sf 2005.

\item \bf Robert Kitt. \it Generalised Scale-Invariance in Financial Time
  Series. \sf 2005.

\item \bf Juss Pavelson. \it Mesoscale Physical Processes and the Related
  Impact on the Summer Nutrient Fields and Phytoplankton Blooms in the
  Western Gulf of Finland. \sf 2005.

\item \bf Olari Ilison. \it Solitons and Solitary Waves in Media with Higher
  Order Dispersive and Nonlinear Effects. \sf 2005.

\item \bf Maksim S\"akki. \it Intermittency and Long-Range Structurization of
  Heart Rate. \sf 2005.

\item \bf Enli Kiipli. \it Modelling Seawater Chemistry of the East Baltic
  Basin in the Late Ordovician–Early Silurian. \sf 2005.

\item \bf Igor Golovtsov. \it Modification of Conductive Properties and
  Processability of Polyparaphenylene, Polypyrrole and
  polyaniline. \sf 2005.

\item \bf Katrin Laos. \it Interaction Between Furcellaran and the Globular
  Proteins (Bovine Serum Albumin $\beta$-Lactoglobulin). \sf 2005.

\item \bf Arvo Mere. \it Structural and Electrical Properties of Spray
  Deposited Copper Indium Disulphide Films for Solar Cells. \sf 2006.

\item \bf Sille Ehala. \it Development and Application of Various On- and
  Off-Line Analytical Methods for the Analysis of Bioactive
  Compounds. \sf 2006.

\item \bf Maria Kulp. \it Capillary Electrophoretic Monitoring of Biochemical
  Reaction Kinetics. \sf 2006.

\item \bf Anu Aasp\~ollu. \it Proteinases from Vipera lebetina Snake Venom
  Affecting Hemostasis. \sf 2006.

\item \bf Lyudmila Chekulayeva. \it Photosensitized Inactivation of Tumor
  Cells by Porphyrins and Chlorins. \sf 2006.

\item \bf Merle Uudsemaa. \it Quantum-Chemical Modeling of Solvated First Row
  Transition Metal Ions. \sf 2006.

\item \bf Tagli Pitsi. \it Nutrition Situation of Pre-School Children in
  Estonia from 1995 to 2004. \sf 2006.

\item \bf Angela Ivask. \it Luminescent Recombinant Sensor Bacteria for the
  Analysis of Bioavailable Heavy Metals. \sf 2006.

\item \bf Tiina L\~ougas. \it Study on Physico-Chemical Properties and Some
  Bioactive Compounds of Sea Buckthorn (Hippophae rhamnoides
  L.). \sf 2006.

\item \bf Kaja Kasemets. \it Effect of Changing Environmental Conditions on
  the Fermentative Growth of Saccharomyces cerevisae S288C:
  Auxo-accelerostat Study. \sf 2006.

\item \bf Ildar Nisamedtinov. \it Application of 13C and Fluorescence Labeling
  in Metabolic Studies of Saccharomyces spp. \sf 2006.

\item \bf Alar Leibak. \it On Additive Generalisation of Voronoï’s Theory of
  Perfect Forms over Algebraic Number Fields. \sf 2006.

\item \bf Andri Jagom\"agi. \it Photoluminescence of Chalcopyrite
  Tellurides. \sf 2006.

\item \bf T\~onu Martma. \it Application of Carbon Isotopes to the Study of
  the Ordovician and Silurian of the Baltic. \sf 2006.

\item \bf Marit Kauk. \it Chemical Composition of CuInSe 2 Monograin Powders
  for Solar Cell Application. \sf 2006.

\item \bf Julia Kois. \it Electrochemical Deposition of CuInSe2 Thin Films for
  Photovoltaic Applications. \sf 2006.

\item \bf Ilona Oja A\c{c}ik. \it Sol-Gel Deposition of Titanium Dioxide
  Films. \sf 2007.

\item \bf Tiia Anmann. \it Integrated and Organized Cellular Bioenergetic
  Systems in Heart and Brain. \sf 2007.

\item \bf Katrin Trummal. \it Purification, Characterization and Specificity
  Studies of Metalloproteinases from Vipera lebetina Snake
  Venom. \sf 2007.

\item \bf Gennadi Lessin. \it Biochemical Definition of Coastal Zone Using
  Numerical Modeling and Measurement Data. \sf 2007.

\item \bf Enno Pais. \it Inverse problems to determine non-homogeneous
  degenerate memory kernels in heat flow. \sf 2007.

\item \bf Maria Borissova. \it Capillary Electrophoresis on Alkylimidazolium
  Salts. \sf 2007.

\item \bf Karin Valmsen. \it Prostaglandin Synthesis in the Coral Plexaura
  homomalla: Control of Prostaglandin Stereochemistry at Carbon 15 by
  Cyclooxygenases. \sf 2007.

\item \bf Kristjan Piirim\"ae. \it Long-Term Changes of Nutrient Fluxes in the
  Drainage Basin of the Gulf of Finland – Application of the PolFlow
  Model. \sf 2007.

\item \bf Tatjana Dedova. \it Chemical Spray Pyrolysis Deposition of Zinc
  Sulfide Thin Films and Zinc Oxide Nanostructured Layers. \sf 2007.

\item \bf Katrin Tomson. \it Production of Labelled Recombinant Proteins in
  Fed-Batch Systems in Escherichia coli. \sf 2007.

\item \bf Cecilia Sarmiento. \it Suppressors of RNA Silencing in Plants. \sf 2008.

\item \bf Vilja Mardla. \it Inhibition of Platelet Aggregation with
  Combination of Antiplatelet Agents. \sf 2008.

\item \bf Maie Bachmann. \it Effect of Modulated Microwave Radiation on Human
  Resting Electroencephalographic Signal. \sf 2008.

\item \bf Dan H\"uvonen. \it Terahertz Spectroscopy of Low-Dimensional Spin
  Systems. \sf 2008.

\item \bf Ly Villo. \it Stereoselective Chemoenzymatic Synthesis of Deoxy
  Sugar Esters Involving Candida antarctica Lipase B. \sf 2008.

\item \bf Johan Anton. \it Technology of Integrated Photoelasticity for
  Residual Stress Measurement in Glass Articles of Axisymmetric
  Shape. \sf 2008.

\item \bf Olga Volobujeva. \it SEM Study of Selenization of Different Thin
  Metallic Films. \sf 2008.

\item \bf Artur J\~ogi. \it Synthesis of 4’-Substituted 2,3’-dideoxynucleoside
  Analogues. \sf 2008.

\item \bf Mario Kadastik. \it Doubly Charged Higgs Boson Decays and
  Implications on Neutrino Physics. \sf 2008.

\item \bf Fernando P\'erez-Caballero. \it Carbon Aerogels from
  5-Methylresorcinol-Formaldehyde Gels. \sf 2008.

\item \bf Sirje Vaask. \it The Comparability, Reproducibility and Validity of
  Estonian Food Consumption Surveys. \sf 2008.

\item \bf Anna Menaker. \it Electrosynthesized Conducting Polymers,
  Polypyrrole and Poly(3,4-ethylenedioxythiophene), for Molecular
  Imprinting. \sf 2009.

\item \bf Lauri Ilison. \it Solitons and Solitary Waves in Hierarchical
  Korteweg-de Vries Type Systems. \sf 2009.

\item \bf Kaia Ernits. \it Study of In2S3 and ZnS Thin Films Deposited by
  Ultrasonic Spray Pyrolysis and Chemical Deposition. \sf 2009.

\item \bf Veljo Sinivee. \it Portable Spectrometer for Ionizing Radiation
  \mquote{Gammamapper}. \sf 2009.

\item \bf J\"uri Virkepu. \it On Lagrange Formalism for Lie Theory and
  Operadic Harmonic Oscillator in Low Dimensions. \sf 2009.

\item \bf Marko Piirsoo. \it Deciphering Molecular Basis of Schwann Cell
  Development. \sf 2009.

\item \bf Kati Helmja. \it Determination of Phenolic Compounds and Their
  Antioxidative Capability in Plant Extracts. \sf 2010.

\item \bf Merike S\~omera. \it Sobemoviruses: Genomic Organization, Potential
  for Recombination and Necessity of P1 in Systemic Infection. \sf 2010.

\item \bf Kristjan Laes. \it Preparation and Impedance Spectroscopy of Hybrid
  Structures Based on CuIn3Se5 Photoabsorber. \sf 2010.

\item \bf Kristin Lippur. \it Asymmetric Synthesis of 2,2’-Bimorpholine and
  its 5,5’-Substituted Derivatives. \sf 2010.

\item \bf Merike Luman. \it Dialysis Dose and Nutrition Assessment by an
  Optical Method. \sf 2010.

\item \bf Mihhail Berezovski. \it Numerical Simulation of Wave Propagation in
  Heterogeneous and Microstructured Materials. \sf 2010.

\item \bf Tamara Aid-Pavlidis. \it Structure and Regulation of BDNF
  Gene. \sf 2010.

\item \bf Olga Bragina. \it The Role of Sonic Hedgehog Pathway in Neuro- and
  Tumorigenesis. \sf 2010.

\item \bf Merle Randr\"u\"ut. \it Wave Propagation in Microstructured Solids:
  Solitary and Periodic Waves. \sf 2010.

\item \bf Marju Laars. \it Asymmetric Organocatalytic Michael and Aldol
  Reactions Mediated by Cyclic Amines. \sf 2010.

\item \bf Maarja Grossberg. \it Optical Properties of Multinary Semiconductor
  Compounds for Photovoltaic Applications. \sf 2010.

\item \bf Alla Maloverjan. \it Vertebrate Homologues of Drosophila Fused
  Kinase and Their Role in Sonic Hedgehog Signalling Pathway. \sf 2010.

\item \bf Priit Pruunsild. \it Neuronal Activity-Dependent Transcription
  Factors and Regulation of Human BDNF Gene. \sf 2010.

\item \bf Tatjana Knjazeva. \it New Approaches in Capillary Electrophoresis
  for Separation and Study of Proteins. \sf 2011.

\item \bf Atanas Katerski. \it Chemical Composition of Sprayed Copper Indium
  Disulfide Films for Nanostructured Solar Cells. \sf 2011.

\item \bf Kristi Timmo. \it Formation of Properties of CuInSe2 and
  Cu2ZnSn(S,Se)4 Monograin Powders Synthesized in Molten KI. \sf 2011.

\item \bf Kert Tamm. \it Wave Propagation and Interaction in Mindlin-Type
  Microstructured Solids: Numerical Simulation. \sf 2011.

\item \bf Adrian Popp. \it Ordovician Proetid Trilobites in Baltoscandia and
  Germany. \sf 2011.

\item \bf Ove P\"arn. \it Sea Ice Deformation Events in the Gulf of Finland
  and This Impact on Shipping. \sf 2011.

\item \bf Germo V\"ali. \it Numerical Experiments on Matter Transport in the
  Baltic Sea. \sf 2011.

\item \bf Andrus Seiman. \it Point-of-Care Analyser Based on Capillary
  Electrophoresis. \sf 2011.

\item \bf Olga Katargina. \it Tick-Borne Pathogens Circulating in Estonia
  (Tick-Borne Encephalitis Virus, Anaplasma phagocytophilum, Babesia
  Species): Their Prevalence and Genetic Characterization. \sf 2011.

\item \bf Ingrid Sumeri. \it The Study of Probiotic Bacteria in Human
  Gastrointestinal Tract Simulator. \sf 2011.

\item \bf Kairit Zovo. \it Functional Characterization of Cellular Copper
  Proteome. \sf 2011.

\item \bf Natalja Makarytsheva. \it Analysis of Organic Species in Sediments
  and Soil by High Performance Separation Methods. \sf 2011.

\item \bf Monika Mortimer. \it Evaluation of the Biological Effects of
  Engineered Nanoparticles on Unicellular Pro- and Eukaryotic
  Organisms. \sf 2011.

\item \bf Kersti Tepp. \it Molecular System Bioenergetics of Cardiac Cells:
  Quantitative Analysis of Structure-Function Relationship. \sf 2011.

\item \bf Anna-Liisa Peikolainen. \it Organic Aerogels Based on
  5-Methylresorcinol. \sf 2011.

\item \bf Leeli Amon. \it Palaeoecological Reconstruction of Late-Glacial
  Vegetation Dynamics in Eastern Baltic Area: A View Based on Plant
  Macrofossil Analysis. \sf 2011.

\item \bf Tanel Peets. \it Dispersion Analysis of Wave Motion in
  Microstructured Solids. \sf 2011.

\item \bf Liina Kaupmees. \it Selenization of Molybdenum as Contact Material
  in Solar Cells. \sf 2011.

\item \bf Allan Olspert. \it Properties of VPg and Coat Protein of
  Sobemoviruses. \sf 2011.

\item \bf Kadri Koppel. \it Food Category Appraisal Using Sensory
  Methods. \sf 2011.

\item \bf Jelena Gorbat\u{s}ova. \it Development of Methods for CE Analysis of
  Plant Phenolics and Vitamins. \sf 2011.

\item \bf Karin Viipsi. \it Impact of EDTA and Humic Substances on the Removal
  of Cd and Zn from Aqueous Solutions by Apatite. \sf 2012.

\item \bf David W. Schryer. \it Metabolic Flux Analysis of Compartmentalized
  Systems using Dynamic Isotopologue Modeling. \sf 2012

\end{list}
%\end{enumerate}
